---
title: "LBW"
author: "Teena Thomas"
date: "2024-02-22"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Loading necessary library

```{r}
library(haven)
library (survey)
library(sf)
library(tmap)
library(ggplot2)
library(dplyr)
library(survey)
library(rnaturalearth)
library(rnaturalearthdata)
library(tidyverse)
```


# Reading data

```{r}
data <- read_dta("IAKR7EFL.DTA")
head (data)
```
```{r}
length(data$m19)
```

```{r}
length(data$b0)
```


```{r}
# Load necessary library
library(dplyr)

# Filter data where b0 equals 1 and select caseid
caseid_b0_1 <- data %>%
  filter(b0 == 0) %>%
  select(caseid)

# View the results
caseid_b0_1

```



# Descriptive Statistics

## Creating subset of data with the relevant variables

```{r}
# All the relevant variables for the analysis has been included in the data subset
relevant_columns <- c("caseid","v005", "v021", "v022", "v023", "v024", "v012", "v130", "v131","sdist", "v437", "v438", "m18", "m19", "b4", "b0", "s220a", "v201")
```



## Checking the NA values in the subset data

```{r}
subset_data <- data %>% select(all_of(relevant_columns))

# Calculate the sum of NA values in each column for the subset
null_values_sum_subset <- colSums(is.na(subset_data))

# Print the sum of null values in each column for the subset
print("Sum of Not Applicable values in each column (subset):")
print(null_values_sum_subset)
```


## Checking the special codes in the subset data

```{r}

# Calculate the percentage of "Don't Know" cases for m18
m18_dk_percent <- mean(subset_data$m18 == 8, na.rm = TRUE) * 100
cat("Percentage of 'Don't Know' cases in m18:", round(m18_dk_percent, 2), "%\n")

# Calculate the percentage of "Don't Know" cases for v131
v131_dk_percent <- mean(subset_data$v131 == 998, na.rm = TRUE) * 100
cat("Percentage of 'Don't Know' cases in v131:", round(v131_dk_percent, 2), "%\n")


# Calculate the percentage of special codes for v438
v438_np_percent <- mean(subset_data$v438 == 9994, na.rm = TRUE) * 100
v438_ref_percent <- mean(subset_data$v438 == 9995, na.rm = TRUE) * 100
v438_oth_percent <- mean(subset_data$v438 == 9996, na.rm = TRUE) * 100
cat("Percentage of special codes in v438:\n")
cat("- Not Present (9994):", round(v438_np_percent, 2), "%\n")
cat("- Refused (9995):", round(v438_ref_percent, 2), "%\n")
cat("- Other (9996):", round(v438_oth_percent, 2), "%\n")

# Calculate the percentage of special codes for v437
v437_np_percent <- mean(subset_data$v437 == 9994, na.rm = TRUE) * 100
v437_ref_percent <- mean(subset_data$v437 == 9995, na.rm = TRUE) * 100
v437_oth_percent <- mean(subset_data$v437 == 9996, na.rm = TRUE) * 100
cat("Percentage of special codes in v437:\n")
cat("- Not Present (9994):", round(v437_np_percent, 2), "%\n")
cat("- Refused (9995):", round(v437_ref_percent, 2), "%\n")
cat("- Other (9996):", round(v437_oth_percent, 2), "%\n")
```


## Checking the birth weight data values

```{r}
m19_counts <- data %>%
summarise(
count_9996 = sum(m19 == 9996, na.rm = TRUE),
count_9998 = sum(m19 == 9998, na.rm = TRUE),
)
print(m19_counts)

```

## Cleaning the data through complete case analysis


```{r}
unique (subset_data$v437)
```

```{r}
unique (subset_data$v438)
```



```{r}
# Convert the weight values to actual kilograms
subset_data$v437 <- subset_data$v437 / 10

# Convert the height values to actual centimeters
subset_data$v438 <- subset_data$v438 / 10

# Print the first few converted weights and heights to verify
print(head(subset_data$v437))
print(head(subset_data$v438))
```


```{r}
# Replace special codes with NA
cleaned_data <- subset_data %>%
  mutate(
    m18 = na_if(m18, 8),
    v131 = na_if(v131, 998),
    v438 = na_if(v438, 9994),
    v438 = na_if(v438, 9995),
    v438 = na_if(v438, 9996),
    v437 = na_if(v437, 9994),
    v437 = na_if(v437, 9995),
    v437 = na_if(v437, 9996),
    m19 = na_if(m19, 9996),
    m19 = na_if(m19, 9998)
  )
```


```{r}
# Verify that special codes are replaced with NA
null_values_sum_subset <- colSums(is.na(cleaned_data))
print("Sum of NA values in each column (subset):")
print(null_values_sum_subset)
```


```{r}
# Additional checks for percentages of NA values 
m18_dk_percent <- mean(is.na(cleaned_data$m18)) * 100
cat("Percentage of NA values in m18:", round(m18_dk_percent, 2), "%\n")

v131_dk_percent <- mean(is.na(cleaned_data$v131)) * 100
cat("Percentage of NA values in v131:", round(v131_dk_percent, 2), "%\n")

v438_na_percent <- mean(is.na(cleaned_data$v438)) * 100
cat("Percentage of NA values in v438:", round(v438_na_percent, 2), "%\n")

v437_na_percent <- mean(is.na(cleaned_data$v437)) * 100
cat("Percentage of NA values in v437:", round(v437_na_percent, 2), "%\n")

m19_na_percent <- mean(is.na(cleaned_data$m19)) * 100
cat("Percentage of NA values in m19:", round(m19_na_percent, 2), "%\n")

```

```{r}
dataset_dimensions <- dim(cleaned_data)
number_of_rows <- nrow(cleaned_data)
number_of_columns <- ncol(cleaned_data)
print(paste("Number of rows:", number_of_rows))
print(paste("Number of columns:", number_of_columns))
```


```{r}
# Define the relevant columns
categorical_columns <- c( "v130", "v131", "m18","b4","b0")

continuous_columns <- c("v012", "m19", "v437", "v438", "s220a", "v201")
```



```{r}
continuous_summary <- cleaned_data %>%
  select(all_of(continuous_columns)) %>%
  summarise_all(list(mean = ~mean(., na.rm = TRUE), 
                     median = ~median(., na.rm = TRUE), 
                     sd = ~sd(., na.rm = TRUE)))

print(continuous_summary)
```


```{r}
for (col in continuous_columns) {
  print(
    ggplot(cleaned_data, aes_string(x = col)) +
      geom_histogram(binwidth = 30) +
      labs(title = paste("Histogram of", col), x = col, y = "Frequency")
  )
}
```


```{r}
# Box plots for continuous variables by low birth weight status (assume M19 is birth weight)
cleaned_data$LBW <- ifelse(cleaned_data$m19 < 2500, "Low Birth Weight", "Normal Birth Weight")

for (col in continuous_columns) {
  print(
    ggplot(cleaned_data, aes_string(x = "LBW", y = col)) +
      geom_boxplot() +
      labs(title = paste("Box plot of", col, "by LBW status"), x = "LBW status", y = col)
  )
}
```



```{r}
# Assuming b4 = 1 represents Male and b4 = 2 represents Female
cleaned_data$sex <- ifelse(cleaned_data$b4 == 1, "Male", "Female")

ggplot(cleaned_data, aes(x = factor(sex), y = m19)) +
  geom_boxplot(fill = "blue", color = "black", alpha = 0.7) +
  labs(title = "Box Plot of Birth Weight by Sex of Child", x = "Sex of Child", y = "Birth Weight (g)")
```



```{r}
ggplot(cleaned_data, aes(x = v012, y = m19)) +
  geom_point(color = "blue", alpha = 0.7) +
  geom_smooth(method = "lm", se = FALSE, color = "red") +
  labs(title = "Scatter Plot of Birth Weight vs. Respondent's Age", x = "Respondent's Age", y = "Birth Weight (g)")

```

```{r}
for (col in categorical_columns) {
  if (length(unique(cleaned_data[[col]])) <= 20) {  # Only plot if unique levels are less than or equal to 20
    print(
      ggplot(data = as.data.frame(categorical_freq_tables[[col]]), aes(x = factor(Var1), y = Freq)) +
        geom_bar(stat = "identity") +
        labs(title = paste("Bar chart of", col), x = col, y = "Count") +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))
    )
  }
}
```



# Design Based Approach


```{r}
# Filtered the 9996 and 9998 from m19 values and included only single births and filtered out twins or multiple births

LBW_analysis <- cleaned_data %>%
  filter(b0 == 0) %>%            
  filter(!is.na(m19))            

```



```{r}
m19_counts <- LBW_analysis %>%
  summarise(
    count_NA = sum(is.na(m19))
  )

print(m19_counts)
```

```{r}
LBW_analysis
```

## SGA Analysis using GROW


```{r}
# Load necessary libraries
library(dplyr)


# Coefficients
constant <- 3455.6
median_height <- 163
median_weight <- 64
ethnic_adjustment <- -149.4

# Function to calculate TOW
calculate_TOW <- function(height, weight, parity, sex) {
  htao <- 6.7 * (height - median_height)
  wtao <- 9.1733 * (weight - median_weight) - 0.151 * (weight - median_weight)^2 - 0.001 * (weight - median_weight)^3
  parao <- case_when(
    parity == 1 ~ 101.9,
    parity == 2 ~ 133.7,
    parity == 3 ~ 140.2,
    parity >= 4 ~ 162.7
  )
  sexao <- ifelse(sex == 1, 48.9, -48.9)
  
  TOW <- constant + htao + wtao + ethnic_adjustment + parao + sexao
  return(TOW)
}

# Calculate TOW for each row
LBW_analysis <- LBW_analysis %>%
  rowwise() %>%
  mutate(TOW = calculate_TOW(v438, v437, v201, b4))
```


```{r}
LBW_analysis
```

```{r}
LBW_analysis <- LBW_analysis %>%
  mutate(GA = s220a * 4.33) 

LBW_analysis
```



```{r}
# Proportionality equation to calculate GROW
calculate_GROW <- function(TOW, GA) {
  percentage_weight <- 298.8 - 31.85 * GA + 1.094 * GA^2 - 0.01055 * GA^3
  GROW <- TOW * (percentage_weight / 100)
  return(GROW)
}
```

```{r}
LBW_analysis <- LBW_analysis %>%
  mutate(GROW = calculate_GROW(TOW, GA))

# Display the results
print(LBW_analysis)

```

```{r}
# Calculate the 10th percentile of GROW (GROW * 0.8592)
LBW_analysis <- LBW_analysis %>%
  mutate(GROW_10th_percentile = GROW * 0.8592)

# Label as "SGA" or "Not SGA"
LBW_analysis <- LBW_analysis %>%
  mutate(SGA = ifelse(m19 < GROW_10th_percentile, "SGA", "Not SGA"))

```


```{r}
LBW_analysis
```


```{r}
library(survey)

# Create survey design
survey_design <- svydesign(id = ~v021, strata = ~v022, weights = ~v005, data = LBW_analysis, nest = TRUE)
options(survey.lonely.psu = "adjust")

```



```{r}
# Calculate overall prevalence of SGA
sga_prevalence <- svymean(~factor(SGA, levels = c("SGA", "Not SGA")), design = survey_design, na.rm = TRUE)

# Extract prevalence and standard errors for SGA
sga_prevalence_true <- coef(sga_prevalence)["factor(SGA, levels = c(\"SGA\", \"Not SGA\"))SGA"] * 100
sga_prevalence_se <- SE(sga_prevalence)["factor(SGA, levels = c(\"SGA\", \"Not SGA\"))SGA"] * 100

# Print results
cat("Overall Prevalence of Small for Gestational Age (SGA):", round(sga_prevalence_true, 2), "%\n")
cat("Standard Error:", round(sga_prevalence_se, 2), "%\n\n")

```

```{r}
# Calculate state-level prevalence of SGA
state_sga_prevalence <- svyby(~factor(SGA, levels = c("SGA", "Not SGA")), ~v024, design = survey_design, svymean, na.rm = TRUE)

# Calculate district-level prevalence of SGA
district_sga_prevalence <- svyby(~factor(SGA, levels = c("SGA", "Not SGA")), ~sdist, design = survey_design, svymean, na.rm = TRUE)
```


```{r}
# Renaming and converting columns in state_sga_prevalence
state_sga_prevalence <- state_sga_prevalence %>%
  mutate(
    `factor(SGA, levels = c("SGA", "Not SGA"))SGA` = `factor(SGA, levels = c("SGA", "Not SGA"))SGA` * 100,
    `se.factor(SGA, levels = c("SGA", "Not SGA"))SGA` = `se.factor(SGA, levels = c("SGA", "Not SGA"))SGA` * 100
  ) %>%
  rename(
    `prevalence of SGA` = `factor(SGA, levels = c("SGA", "Not SGA"))SGA`,
    `standard error of SGA` = `se.factor(SGA, levels = c("SGA", "Not SGA"))SGA`
  )

# Renaming and converting columns in district_sga_prevalence
district_sga_prevalence <- district_sga_prevalence %>%
  mutate(
    `factor(SGA, levels = c("SGA", "Not SGA"))SGA` = `factor(SGA, levels = c("SGA", "Not SGA"))SGA` * 100,
    `se.factor(SGA, levels = c("SGA", "Not SGA"))SGA` = `se.factor(SGA, levels = c("SGA", "Not SGA"))SGA` * 100
  ) %>%
  rename(
    `prevalence of SGA` = `factor(SGA, levels = c("SGA", "Not SGA"))SGA`,
    `standard error of SGA` = `se.factor(SGA, levels = c("SGA", "Not SGA"))SGA`
  )

# Print results
print(state_sga_prevalence)
print(district_sga_prevalence)

```


```{r}
# Load necessary libraries
library(dplyr)
library(sf)
library(ggplot2)
library(viridis)
library(leaflet)
library(htmltools)

# Load the state-level shapefile from GADM
india_states <- st_read("gadm41_IND_1.json")

# Check the unique state names in the shapefile
unique_states <- unique(india_states$NAME_1)
print(unique_states)

# Create a mapping for the state names
state_mapping <- data.frame(
  v024 = c(1:24, 25, 25, 27:36),
  state_name = c("JammuandKashmir", "HimachalPradesh", "Punjab", "Chandigarh", 
                 "Uttarakhand", "Haryana", "NCTofDelhi", "Rajasthan", "UttarPradesh", 
                 "Bihar", "Sikkim", "ArunachalPradesh", "Nagaland", "Manipur", 
                 "Mizoram", "Tripura", "Meghalaya", "Assam", "WestBengal", "Jharkhand", 
                 "Odisha", "Chhattisgarh", "MadhyaPradesh", "Gujarat", 
                 "DadraandNagarHaveliandDamanandDiu", "DadraandNagarHaveliandDamanandDiu", "Maharashtra", "AndhraPradesh", 
                 "Karnataka", "Goa", "Lakshadweep", "Kerala", "TamilNadu", 
                 "Puducherry", "AndamanandNicobar", "Telangana"),
  stringsAsFactors = FALSE
)

# Join this mapping to the SGA prevalence data
state_sga_prevalence <- state_sga_prevalence %>%
  mutate(v024 = ifelse(v024 == 25, 25, v024)) %>%
  left_join(state_mapping, by = "v024") %>%
  select(state_name, `prevalence of SGA`, `standard error of SGA`)

# Combine Dadra and Nagar Haveli and Daman and Diu in the spatial data
india_states <- india_states %>%
  mutate(NAME_1 = ifelse(NAME_1 %in% c("DadraandNagarHaveli", "DamanandDiu"), "DadraandNagarHaveliandDamanandDiu", NAME_1))

# Combine prevalence data for Dadra and Nagar Haveli and Daman and Diu
state_sga_prevalence <- state_sga_prevalence %>%
  group_by(state_name) %>%
  summarize(prevalence = mean(`prevalence of SGA`, na.rm = TRUE), se = mean(`standard error of SGA`, na.rm = TRUE))

# Join the standardized state names with the spatial data
india_states <- india_states %>%
  left_join(state_sga_prevalence, by = c("NAME_1" = "state_name"))

# Remove Ladakh from the dataset because Ladakh is not there in the NFHS data
india_states <- india_states %>%
  filter(NAME_1 != "Ladakh")

# Plot the map
ggplot(india_states) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "SGA Prevalence by State in India",
       fill = "Prevalence (%)") +
  theme_minimal()
```


```{r}
# Calculate the upper and lower bounds of the confidence intervals
india_states <- india_states %>%
  mutate(
    lower_bound = prevalence - 1.96 * se,
    upper_bound = prevalence + 1.96 * se
  )

# Create labels with HTML formatting
india_states$label <- paste0(
  "State: <strong>", india_states$NAME_1, "</strong><br>",
  "Prevalence: <strong>", round(india_states$prevalence, 2), "%</strong><br>",
  "95% CI: <strong>", round(india_states$lower_bound, 2), "% - ", round(india_states$upper_bound, 2), "%</strong>"
)

# Wrap label content with HTML function
india_states$label <- lapply(india_states$label, htmltools::HTML)

# Plot the interactive map
leaflet(india_states) %>%
  addTiles() %>%
  addPolygons(
    fillColor = ~colorQuantile("Viridis", prevalence)(prevalence),
    weight = 1,
    opacity = 1,
    color = "white",
    dashArray = "3",
    fillOpacity = 0.7,
    label = ~label,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto"
    ),
    highlightOptions = highlightOptions(
      color = "white",
      weight = 2,
      bringToFront = TRUE
    )
  )

```


## SGA Analysis using INTERGROWTH


```{r}
library(readxl)
library(writexl)
library(dplyr)

# Convert gestational age from months to weeks and days
LBW_analysis <- LBW_analysis %>%
  mutate(
    GA_weeks = floor(GA),    # Extract whole weeks
    GA_days = round((GA - GA_weeks) * 7),  # Convert remaining fraction to days
    Gestational_age = paste(GA_weeks, GA_days, sep = "+")  # Format as "weeks+days"
  )
```

```{r}
LBW_analysis
```



```{r}
# Read the Excel template
excel_template <- read_excel("Intergrowth.xlsx", sheet = 1)
```
```{r}
# Prepare the data frame to match the Excel template

excel_data <- data.frame(
  `ID` = LBW_analysis$caseid,
  `Gestational age (weeks+days)` = LBW_analysis$Gestational_age,
  `EFW (g)` = LBW_analysis$m19,
  `v005` = LBW_analysis$v005,
  `v021` = LBW_analysis$v021,
  `v022` = LBW_analysis$v022,
  `v023` = LBW_analysis$v023,
  `v024` = LBW_analysis$v024,
  `v012` = LBW_analysis$v012,
  `v130` = LBW_analysis$v130,
  `v131` = LBW_analysis$v131,
  `sdist` = LBW_analysis$sdist,
  `v437` = LBW_analysis$v437,
  `v438` = LBW_analysis$v438,
  `m18` = LBW_analysis$m18,
  `m19` = LBW_analysis$m19,
  `b4` = LBW_analysis$b4,
  `b0` = LBW_analysis$b0,
  `s220a` = LBW_analysis$s220a,
  `v201` = LBW_analysis$v201,
  `TOW` = LBW_analysis$TOW,
  `GROW` = LBW_analysis$GROW,
  `GROW_10th_percentile` = LBW_analysis$GROW_10th_percentile,
  `GROW_SGA` = LBW_analysis$SGA
)


# Assuming the template starts at row 2 (row 1 being the header)
# Adjust the row number if your template structure is different
start_row <- 4

# Write the data to the Excel template
write_xlsx(excel_data, "Intergrowth_Updates.xlsx")

```


```{r}
# Load necessary libraries
library(readxl)
library(dplyr)

# Read the Excel file
intergrowth_data <- read_excel("Intergrowth_SGA.xlsx")

# Calculate SGA status
intergrowth_data <- intergrowth_data %>%
  mutate(Intergrowth_SGA = ifelse(centile < 10, "SGA", "Not SGA"))

# View the updated data with SGA status
print(intergrowth_data)

# Save the updated data to a new Excel file
write_xlsx(intergrowth_data, "Intergrowth_results_with_SGA.xlsx")

```


```{r}
intergrowth_data <- read_excel("Intergrowth_results_with_SGA.xlsx", sheet = 1)
```

```{r}
intergrowth_data
```


```{r}

# Create survey design
survey_design <- svydesign(id = ~v021, strata = ~v022, weights = ~v005, data = intergrowth_data, nest = TRUE)
options(survey.lonely.psu = "adjust")

# Calculate overall prevalence of SGA
Intergrowth_sga_prevalence <- svymean(~factor(Intergrowth_SGA, levels = c("SGA", "Not SGA")), design = survey_design, na.rm = TRUE)

# Extract prevalence and standard errors for SGA
Intergrowth_sga_prevalence_true <- coef(Intergrowth_sga_prevalence)["factor(Intergrowth_SGA, levels = c(\"SGA\", \"Not SGA\"))SGA"] * 100
Intergrowth_sga_prevalence_se <- SE(Intergrowth_sga_prevalence)["factor(Intergrowth_SGA, levels = c(\"SGA\", \"Not SGA\"))SGA"] * 100

# Print results
cat("Overall Prevalence of Small for Gestational Age (SGA):", round(Intergrowth_sga_prevalence_true, 2), "%\n")
cat("Standard Error:", round(Intergrowth_sga_prevalence_se, 2), "%\n\n")
```

```{r}
# Calculate state-level prevalence of Intergrowth SGA
state_intergrowth_sga_prevalence <- svyby(~factor(Intergrowth_SGA, levels = c("SGA", "Not SGA")), ~v024, design = survey_design, svymean, na.rm = TRUE)

# Renaming and converting columns in state_intergrowth_sga_prevalence
state_intergrowth_sga_prevalence <- state_intergrowth_sga_prevalence %>%
  mutate(
    `factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA` = `factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA` * 100,
    `se.factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA` = `se.factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA` * 100
  ) %>%
  rename(
    `prevalence of SGA` = `factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA`,
    `standard error of SGA` = `se.factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA`
  )



# Calculate district-level prevalence of SGA
district_intergrowth_sga_prevalence <- svyby(~factor(Intergrowth_SGA, levels = c("SGA", "Not SGA")), ~sdist, design = survey_design, svymean, na.rm = TRUE)


# Renaming and converting columns in district_sga_prevalence
district_intergrowth_sga_prevalence <- district_intergrowth_sga_prevalence %>%
  mutate(
    `factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA` = `factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA` * 100,
    `se.factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA` = `se.factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA` * 100
  ) %>%
  rename(
    `prevalence of SGA` = `factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA`,
    `standard error of SGA` = `se.factor(Intergrowth_SGA, levels = c("SGA", "Not SGA"))SGA`
  )

# Print results
print(state_intergrowth_sga_prevalence)
print(district_intergrowth_sga_prevalence)

```


```{r}
# Join this mapping to the SGA prevalence data
state_intergrowth_sga_prevalence <- state_intergrowth_sga_prevalence %>%
  mutate(v024 = ifelse(v024 == 25, 25, v024)) %>%
  left_join(state_mapping, by = "v024") %>%
  select(state_name, `prevalence of SGA`, `standard error of SGA`)

# Combine Dadra and Nagar Haveli and Daman and Diu in the spatial data
india_states <- india_states %>%
  mutate(NAME_1 = ifelse(NAME_1 %in% c("DadraandNagarHaveli", "DamanandDiu"), "DadraandNagarHaveliandDamanandDiu", NAME_1))

# Combine prevalence data for Dadra and Nagar Haveli and Daman and Diu
state_intergrowth_sga_prevalence <- state_intergrowth_sga_prevalence %>%
  group_by(state_name) %>%
  summarize(prevalence = mean(`prevalence of SGA`, na.rm = TRUE), se = mean(`standard error of SGA`, na.rm = TRUE))

# Join the standardized state names with the spatial data
india_states <- india_states %>%
  left_join(state_intergrowth_sga_prevalence, by = c("NAME_1" = "state_name"))

# Remove Ladakh from the dataset because Ladakh is not there in the NFHS data
india_states <- india_states %>%
  filter(NAME_1 != "Ladakh")
```


```{r}
# Plot the map
ggplot(india_states) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "SGA Prevalence by State in India (Intergrowth)",
       fill = "Prevalence (%)") +
  theme_minimal()
```




## Creating the survey design for the calculation of Low Birth Weight



```{r}
# Create survey design
survey_design <- svydesign(id = ~v021, strata = ~v022, weights = ~v005, data = LBW_analysis, nest = TRUE)

options(survey.lonely.psu = "adjust")

# Calculate overall prevalence of low birth weight (less than 2500 grams)
low_birth_weight <- svymean(~I(m19 < 2500), design = survey_design, na.rm = TRUE)

# Extract prevalence and standard errors
low_birth_weight_true <- coef(low_birth_weight)["I(m19 < 2500)TRUE"] * 100
low_birth_weight_se <- SE(low_birth_weight)["I(m19 < 2500)TRUE"] * 100
```


```{r}
# Calculate state-level prevalence of low birth weight
state_prevalence_true <- svyby(~I(m19 < 2500), ~v024, design = survey_design, svymean, na.rm = TRUE)

# Calculate district-level prevalence of low birth weight
district_prevalence_true <- svyby(~I(m19 < 2500), ~sdist, design = survey_design, svymean, na.rm = TRUE)
```


```{r}
state_prevalence_true
district_prevalence_true
```


```{r}
# Convert proportions to percentages in state_prevalence_true
state_prevalence_true <- state_prevalence_true %>%
  mutate(
    `I(m19 < 2500)FALSE` = `I(m19 < 2500)FALSE` * 100,
    `I(m19 < 2500)TRUE` = `I(m19 < 2500)TRUE` * 100,
    `se.I(m19 < 2500)FALSE` = `se.I(m19 < 2500)FALSE` * 100,
    `se.I(m19 < 2500)TRUE` = `se.I(m19 < 2500)TRUE` * 100
  )

# Convert proportions to percentages in district_prevalence_true
district_prevalence_true <- district_prevalence_true %>%
  mutate(
    `I(m19 < 2500)FALSE` = `I(m19 < 2500)FALSE` * 100,
    `I(m19 < 2500)TRUE` = `I(m19 < 2500)TRUE` * 100,
    `se.I(m19 < 2500)FALSE` = `se.I(m19 < 2500)FALSE` * 100,
    `se.I(m19 < 2500)TRUE` = `se.I(m19 < 2500)TRUE` * 100
  )

```


```{r}
state_prevalence_true
district_prevalence_true
```


```{r}
# Print results
cat("Overall Prevalence of Low Birth Weight (LBW):", round(low_birth_weight_true, 2), "%\n")
cat("Standard Error:", round(low_birth_weight_se, 2), "%\n\n")
```




## Creating Maps for low birth weight prevelance at the state level

```{r}
# Loaded state-level shapefile from GADM
india_states <- st_read("gadm41_IND_1.json")
```

```{r}
unique_states <- unique(india_states$NAME_1)
print(unique_states)
```


```{r}
# Created a mapping for the state names
state_mapping <- data.frame(
  v024 = c(1:24, 25, 25, 27:36),
  state_name = c("JammuandKashmir", "HimachalPradesh", "Punjab", "Chandigarh", 
                 "Uttarakhand", "Haryana", "NCTofDelhi", "Rajasthan", "UttarPradesh", 
                 "Bihar", "Sikkim", "ArunachalPradesh", "Nagaland", "Manipur", 
                 "Mizoram", "Tripura", "Meghalaya", "Assam", "WestBengal", "Jharkhand", 
                 "Odisha", "Chhattisgarh", "MadhyaPradesh", "Gujarat", 
                 "DadraandNagarHaveliandDamanandDiu", "DadraandNagarHaveliandDamanandDiu", "Maharashtra", "AndhraPradesh", 
                 "Karnataka", "Goa", "Lakshadweep", "Kerala", "TamilNadu", 
                 "Puducherry", "AndamanandNicobar", "Telangana"),
  stringsAsFactors = FALSE
)

# Combining Dadra and Nagar Haveli and Daman and Diu in the prevalence data because this is mentioned as one state in the NFHS dataset and as seperate in the GADM file
state_prevalence_true <- state_prevalence_true %>%
  mutate(v024 = ifelse(v024 == 25, 25, v024))

# Join this mapping to the prevalence_by_state data
state_prevalence_true <- state_prevalence_true %>%
  left_join(state_mapping, by = "v024") %>%
  select(state_name, `I(m19 < 2500)TRUE`, `se.I(m19 < 2500)TRUE`) %>%
  rename(prevalence = `I(m19 < 2500)TRUE`, se = `se.I(m19 < 2500)TRUE`)

# Combined Dadra and Nagar Haveli and Daman and Diu in the spatial data
india_states <- india_states %>%
  mutate(NAME_1 = ifelse(NAME_1 %in% c("DadraandNagarHaveli", "DamanandDiu"), "DadraandNagarHaveliandDamanandDiu", NAME_1))

# Combine prevalence data for Dadra and Nagar Haveli and Daman and Diu
state_prevalence_true <- state_prevalence_true %>%
  group_by(state_name) %>%
  summarize(prevalence = mean(prevalence, na.rm = TRUE), se = mean(se, na.rm = TRUE))

# Join the standardized state names with the spatial data
india_states <- india_states %>%
  left_join(state_prevalence_true, by = c("NAME_1" = "state_name"))

# Removed Ladakh from the dataset because Ladakh is not there in the NFHS data
india_states <- india_states %>%
  filter(NAME_1 != "Ladakh")


# Plot the map
ggplot(india_states) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "Low Birth Weight Prevalence by State in India",
       fill = "Prevalence (%)") +
  theme_minimal()


```



```{r}
# Calculate the upper and lower bounds of the confidence intervals
india_states <- india_states %>%
mutate(
lower_bound = prevalence - 1.96 * se,
upper_bound = prevalence + 1.96 * se
)
```



```{r}
library(leaflet)
library(htmltools)


# Create labels with HTML formatting
india_states$label <- paste0(
  "State: <strong>", india_states$NAME_1, "</strong><br>",
  "Prevalence: <strong>", round(india_states$prevalence, 2), "%</strong><br>",
  "95% CI: <strong>", round(india_states$lower_bound, 2), "% - ", round(india_states$upper_bound, 2), "%</strong>"
)

# Wrap label content with HTML function
india_states$label <- lapply(india_states$label, htmltools::HTML)


leaflet(india_states) %>%
addTiles() %>%
addPolygons(
fillColor = ~colorQuantile("Viridis", prevalence)(prevalence),
weight = 1,
opacity = 1,
color = "white",
dashArray = "3",
fillOpacity = 0.7,
label = ~label,
labelOptions = labelOptions(
style = list("font-weight" = "normal", padding = "3px 8px"),
textsize = "15px",
direction = "auto"
),
highlightOptions = highlightOptions(
color = "white",
weight = 2,
bringToFront = TRUE
)
)
```



## Creating Maps for low birth weight prevelance at the district level

```{r}
india_districts <- st_read("gadm41_IND_2.json")
head(india_districts)
```


```{r}
unique(india_districts$NAME_2)
```


```{r}
# Create a vector with all the district names
nfhs_district_names <- c(
  "Kupwara", "Badgam", "Leh(Ladakh)", "Kargil", "Punch", "Rajouri", "Kathua", "Baramula", "Bandipore", "Srinagar", 
  "Ganderbal", "Pulwama", "Shupiyan", "Anantnag", "Kulgam", "Doda", "Ramban", "Kishtwar", "Udhampur", "Reasi", 
  "Jammu", "Samba", "Chamba", "Kangra", "Lahul & Spiti", "Kullu", "Mandi", "Hamirpur", "Una", "Bilaspur", 
  "Solan", "Sirmaur", "Shimla", "Kinnaur", "Kapurthala", "Jalandhar", "Hoshiarpur", "Shahid Bhagat Singh Nagar", 
  "Fatehgarh Sahib", "Ludhiana", "Moga", "Muktsar", "Faridkot", "Bathinda", "Mansa", "Patiala", "Amritsar", 
  "Tarn Taran", "Rupnagar", "Sahibzada Ajit Singh Nagar", "Sangrur", "Barnala", "Chandigarh", "Uttarkashi", 
  "Chamoli", "Rudraprayag", "Tehri Garhwal", "Dehradun", "Garhwal", "Pithoragarh", "Bageshwar", "Almora", 
  "Champawat", "Nainital", "Udham Singh Nagar", "Hardwar", "Panchkula", "Ambala", "Yamunanagar", "Kurukshetra", 
  "Kaithal", "Karnal", "Panipat", "Sonipat", "Jind", "Fatehabad", "Sirsa", "Hisar", "Rohtak", "Jhajjar", 
  "Mahendragarh", "Rewari", "Gurgaon", "Mewat", "Faridabad", "Palwal", "Ganganagar", "Hanumangarh", "Bikaner", 
  "Churu", "Jhunjhunun", "Alwar", "Bharatpur", "Dhaulpur", "Karauli", "Sawai Madhopur", "Dausa", "Jaipur", 
  "Sikar", "Nagaur", "Jodhpur", "Jaisalmer", "Barmer", "Jalor", "Sirohi", "Pali", "Ajmer", "Tonk", "Bundi", 
  "Bhilwara", "Rajsamand", "Dungarpur", "Banswara", "Chittaurgarh", "Kota", "Baran", "Jhalawar", "Udaipur", 
  "Pratapgarh", "Saharanpur", "Bijnor", "Rampur", "Jyotiba Phule Nagar", "Meerut", "Baghpat", "Gautam Buddha Nagar", 
  "Bulandshahr", "Aligarh", "Mahamaya Nagar", "Mathura", "Agra", "Firozabad", "Mainpuri", "Bareilly", "Pilibhit", 
  "Shahjahanpur", "Kheri", "Sitapur", "Hardoi", "Unnao", "Lucknow", "Farrukhabad", "Kannauj", "Etawah", "Auraiya", 
  "Kanpur Dehat", "Kanpur Nagar", "Jalaun", "Jhansi", "Lalitpur", "Hamirpur", "Mahoba", "Banda", "Chitrakoot", 
  "Fatehpur", "Pratapgarh", "Kaushambi", "Allahabad", "Bara Banki", "Faizabad", "Ambedkar Nagar", "Bahraich", 
  "Shrawasti", "Balrampur", "Gonda", "Siddharthnagar", "Basti", "Sant Kabir Nagar", "Mahrajganj", "Gorakhpur", 
  "Kushinagar", "Deoria", "Azamgarh", "Mau", "Ballia", "Jaunpur", "Ghazipur", "Chandauli", "Varanasi", 
  "Sant Ravidas Nagar (Bhadohi)", "Mirzapur", "Sonbhadra", "Etah", "Kanshiram Nagar", "Pashchim Champaran", 
  "Purba Champaran", "Sheohar", "Sitamarhi", "Madhubani", "Supaul", "Araria", "Kishanganj", "Purnia", 
  "Katihar", "Madhepura", "Saharsa", "Darbhanga", "Muzaffarpur", "Gopalganj", "Siwan", "Saran", "Vaishali", 
  "Samastipur", "Begusarai", "Khagaria", "Bhagalpur", "Banka", "Munger", "Lakhisarai", "Sheikhpura", "Nalanda", 
  "Patna", "Bhojpur", "Buxar", "Kaimur (Bhabua)", "Rohtas", "Aurangabad", "Gaya", "Nawada", "Jamui", "Jehanabad", 
  "Arwal", "North District", "West District", "South District", "East District", "Tawang", "West Kameng", 
  "East Kameng", "Papum Pare", "Upper Subansiri", "Upper Siang", "Changlang", "Lower Subansiri", "Dibang Valley", 
  "Lower Dibang Valley", "Anjaw", "Mon", "Mokokchung", "Zunheboto", "Wokha", "Dimapur", "Phek", "Tuensang", 
  "Longleng", "Kiphire", "Kohima", "Peren", "Senapati", "Tamenglong", "Churachandpur", "Bishnupur", "Thoubal", 
  "Imphal West", "Imphal East", "Ukhrul", "Chandel", "Mamit", "Kolasib", "Aizawl", "Champhai", "Serchhip", 
  "Lunglei", "Lawngtlai", "Saiha", "Dhalai", "South Garo Hills", "Ribhoi", "East Khasi Hills", "Kokrajhar", 
  "Goalpara", "Barpeta", "Morigaon", "Lakhimpur", "Dhemaji", "Tinsukia", "Dibrugarh", "Golaghat", "Dima Hasao", 
  "Cachar", "Karimganj", "Hailakandi", "Bongaigaon", "Chirang", "Kamrup", "Kamrup Metropolitan", "Nalbari", 
  "Baksa", "Darrang", "Udalguri", "Darjiling", "Jalpaiguri", "Koch Bihar", "Uttar Dinajpur", "Dakshin Dinajpur", 
  "Maldah", "Murshidabad", "Birbhum", "Nadia", "North Twenty Four Parganas", "Hugli", "Bankura", "Puruliya", 
  "Haora", "Kolkata", "South Twenty Four Parganas", "Paschim Medinipur", "Purba Medinipur", "Garhwa", "Chatra", 
  "Kodarma", "Giridih", "Deoghar", "Godda", "Sahibganj", "Pakur", "Dhanbad", "Bokaro", "Lohardaga", 
  "Purbi Singhbhum", "Palamu", "Latehar", "Hazaribagh", "Ramgarh", "Dumka", "Jamtara", "Ranchi", "Khunti", 
  "Gumla", "Simdega", "Pashchimi Singhbhum", "Saraikela-Kharsawan", "Bargarh", "Jharsuguda", "Sambalpur", 
  "Debagarh", "Sundargarh", "Kendujhar", "Mayurbhanj", "Baleshwar", "Bhadrak", "Kendrapara", "Jagatsinghapur", 
  "Cuttack", "Jajapur", "Dhenkanal", "Anugul", "Nayagarh", "Khordha", "Puri", "Ganjam", "Gajapati", 
  "Kandhamal", "Baudh", "Subarnapur", "Balangir", "Nuapada", "Kalahandi", "Rayagada", "Nabarangapur", 
  "Koraput", "Malkangiri", "Koriya", "Jashpur", "Raigarh", "Korba", "Janjgir - Champa", "Kabeerdham", 
  "Rajnandgaon", "Mahasamund", "Dhamtari", "Uttar Bastar Kanker", "Narayanpur", "Bijapur", "Sheopur", 
  "Morena", "Bhind", "Gwalior", "Datia", "Shivpuri", "Tikamgarh", "Chhatarpur", "Panna", "Sagar", "Damoh", 
  "Satna", "Rewa", "Umaria", "Neemuch", "Mandsaur", "Ratlam", "Ujjain", "Dewas", "Dhar", "Indore", 
  "Khargone (West Nimar)", "Barwani", "Rajgarh", "Vidisha", "Bhopal", "Sehore", "Raisen", "Betul", 
  "Harda", "Hoshangabad", "Katni", "Jabalpur", "Narsimhapur", "Dindori", "Mandla", "Chhindwara", "Seoni", 
  "Balaghat", "Guna", "Ashoknagar", "Shahdol", "Anuppur", "Sidhi", "Singrauli", "Jhabua", "Alirajpur", 
  "Khandwa (East Nimar)", "Burhanpur", "Kachchh", "Banas Kantha", "Patan", "Mahesana", "Gandhinagar", 
  "Porbandar", "Amreli", "Anand", "Dohad", "Narmada", "Bharuch", "The Dangs", "Navsari", "Valsad", "Surat", 
  "Tapi", "Diu", "Daman", "Dadra & Nagar Haveli", "Nandurbar", "Dhule", "Jalgaon", "Buldana", "Akola", 
  "Washim", "Amravati", "Wardha", "Nagpur", "Bhandara", "Gondiya", "Gadchiroli", "Chandrapur", "Yavatmal", 
  "Nanded", "Hingoli", "Parbhani", "Jalna", "Aurangabad", "Nashik", "Mumbai Suburban", "Mumbai", 
  "Raigarh", "Pune", "Ahmadnagar", "Bid", "Latur", "Osmanabad", "Solapur", "Satara", "Ratnagiri", 
  "Sindhudurg", "Kolhapur", "Sangli", "Srikakulam", "Vizianagaram", "Visakhapatnam", "East Godavari", 
  "West Godavari", "Krishna", "Guntur", "Prakasam", "Sri Potti Sriramulu Nellore", "Y.S.R.", "Kurnool", 
  "Anantapur", "Chittoor", "Belgaum", "Bagalkot", "Bijapur", "Bidar", "Raichur", "Koppal", "Gadag", 
  "Dharwad", "Uttara Kannada", "Haveri", "Bellary", "Chitradurga", "Davanagere", "Shimoga", "Udupi", 
  "Chikmagalur", "Tumkur", "Bangalore", "Mandya", "Hassan", "Dakshina Kannada", "Kodagu", "Mysore", 
  "Chamarajanagar", "Gulbarga", "Yadgir", "Kolar", "Chikkaballapura", "Bangalore Rural", "Ramanagara", 
  "North Goa", "South Goa", "Lakshadweep", "Kasaragod", "Kannur", "Wayanad", "Kozhikode", "Malappuram", 
  "Palakkad", "Thrissur", "Ernakulam", "Idukki", "Kottayam", "Alappuzha", "Pathanamthitta", "Kollam", 
  "Thiruvananthapuram", "Thiruvallur", "Chennai", "Kancheepuram", "Vellore", "Tiruvannamalai", "Viluppuram", 
  "Salem", "Namakkal", "Erode", "The Nilgiris", "Dindigul", "Karur", "Tiruchirappalli", "Perambalur", 
  "Ariyalur", "Cuddalore", "Nagapattinam", "Thiruvarur", "Thanjavur", "Pudukkottai", "Sivaganga", 
  "Madurai", "Theni", "Virudhunagar", "Ramanathapuram", "Thoothukkudi", "Tirunelveli", "Kanniyakumari", 
  "Dharmapuri", "Krishnagiri", "Coimbatore", "Tiruppur", "Yanam", "Puducherry", "Mahe", "Karaikal", 
  "Nicobars", "North & Middle Andaman", "South Andaman", "East Siang", "Kra Daadi", "Kurung Kumey", 
  "Lohit", "Longding", "Namsai", "Siang", "Tirap", "West Siang", "Biswanath", "Charaideo", "Dhubri", 
  "Hojai", "Jorhat", "Karbi Anglong", "Majuli", "Nagaon", "Sivasagar", "Sonitpur", "South Salmara Mancachar", 
  "West Karbi Anglong", "Balod", "Baloda Bazar", "Balrampur", "Bastar", "Bemetara", "Bilaspur", 
  "Dantewada", "Durg", "Gariyaband", "Kodagaon", "Mungeli", "Raipur", "Sukma", "Surajpur", "Surguja", 
  "Central", "East", "New Delhi", "North", "North East", "North West", "Shahdara", "South", "South East", 
  "South West", "West", "Ahmadabad", "Aravali", "Bhavnagar", "Botad", "Chhota Udaipur", "Devbhumi Dwarka", 
  "Gir Somnath", "Jamnagar", "Junagadh", "Kheda", "Mahisagar", "Morbi", "Panch Mahals", "Rajkot", 
  "Sabar Kantha", "Surendranagar", "Vadodara", "Bhiwani", "Charkhi Dadri", "Agar Malwa", "Shajapur", 
  "Palghar", "Thane", "East Garo Hills", "East Jantia Hills", "North Garo Hills", "South West Garo Hills", 
  "South West Khasi Hills", "West Garo Hills", "West Jaintia Hills", "West Khasi Hills", "Fazilka", 
  "Firozpur", "Gurdaspur", "Pathankot", "Adilabad", "Bhadradri Kothagudem", "Hyderabad", "Jagitial", 
  "Jangoan", "Jayashankar Bhupalapally", "Jogulamba Gadwal", "Kamareddy", "Karimnagar", "Khammam", 
  "Komaram Bheem Asifabad", "Mahabubabad", "Mahabubnagar", "Mancherial", "Medak", "Medchal-Malkajgiri", 
  "Nagarkurnool", "Nalgonda", "Nirmal", "Nizamabad", "Peddapalli", "Rajanna Sircilla", "Ranga Reddy", 
  "Sangareddy", "Siddipet", "Suryapet", "Vikarabad", "Wanaparthy", "Warangal Rural", "Warangal Urban", 
  "Yadadri Bhuvanagiri", "Gomati", "Khowai", "North Tripura", "Sepahijala", "South Tripura", "Unakoti", 
  "West Tripura", "Amethi", "Budaun", "Ghaziabad", "Hapur", "Moradabad", "Muzaffarnagar", "Rae Bareli", 
  "Sambhal", "Shamli", "Sultanpur", "Paschim Barddhaman", "Purba Barddhaman"
)

# Create a vector with all the district names
gadm_district_names <- c(
  "NicobarIslands", "NorthandMiddleAndaman", "SouthAndaman", "Anantapur", "Chittoor",
  "EastGodavari", "Guntur", "Krishna", "Kurnool", "Nellore",
  "Prakasam", "Srikakulam", "Visakhapatnam", "Vizianagaram", "WestGodavari",
  "Y.S.R.", "Anjaw", "Changlang", "DibangValley", "EastKameng",
  "EastSiang", "KurungKumey", "Lohit", "Longding", "LowerDibangValley",
  "LowerSubansiri", "Namsai", "PapumPare", "Tawang", "Tirap",
  "UpperSiang", "UpperSubansiri", "WestKameng", "WestSiang", "Baksa",
  "Barpeta", "Bongaigaon", "Cachar", "Chirang", "Darrang",
  "Dhemaji", "Dhubri", "Dibrugarh", "DimaHasao", "Goalpara",
  "Golaghat", "Hailakandi", "Jorhat", "Kamrup", "KamrupMetropolitan",
  "KarbiAnglong", "Karimganj", "Kokrajhar", "Lakhimpur", "Morigaon",
  "Nagaon", "Nalbari", "Sivasagar", "Sonitpur", "Tinsukia",
  "Udalguri", "Araria", "Arwal", "Aurangabad", "Banka",
  "Begusarai", "Bhagalpur", "Bhojpur", "Buxar", "Darbhanga",
  "Gaya", "Gopalganj", "Jamui", "Jehanabad", "Kaimur",
  "Katihar", "Khagaria", "Kishanganj", "Lakhisarai", "Madhepura",
  "Madhubani", "Munger", "Muzaffarpur", "Nalanda", "Nawada",
  "PashchimChamparan", "Patna", "PurbaChamparan", "Purnia", "Rohtas",
  "Saharsa", "Samastipur", "Saran", "Sheikhpura", "Sheohar",
  "Sitamarhi", "Siwan", "Supaul", "Vaishali", "Chandigarh",
  "Balod", "BalodaBazar", "Balrampur", "Bastar", "Bemetara",
  "Bijapur", "Bilaspur", "Dantewada", "Dhamtari", "Durg",
  "Gariaband", "Janjgir-Champa", "Jashpur", "Kabeerdham", "Kondagaon",
  "Korba", "Koriya", "Mahasamund", "Mungeli", "Narayanpur",
  "Raigarh", "Raipur", "Rajnandgaon", "Sukma", "Surajpur",
  "Surguja", "UttarBastarKanker", "DadraandNagarHaveli", "Daman", "Diu",
  "NorthGoa", "SouthGoa", "Ahmadabad", "Amreli", "Anand",
  "Aravalli", "BanasKantha", "Bharuch", "Bhavnagar", "Botad",
  "ChhotaUdaipur", "Dahod", "DevbhumiDwarka", "Gandhinagar", "GirSomnath",
  "Jamnagar", "Junagadh", "Kachchh", "Kheda", "Mahesana",
  "Mahisagar", "Morbi", "Narmada", "Navsari", "PanchMahals",
  "Patan", "Porbandar", "Rajkot", "SabarKantha", "Surat",
  "Surendranagar", "Tapi", "TheDangs", "Vadodara", "Valsad",
  "Ambala", "Bhiwani", "Faridabad", "Fatehabad", "Gurgaon",
  "Hisar", "Jhajjar", "Jind", "Kaithal", "Karnal",
  "Kurukshetra", "Mahendragarh", "Mewat", "Palwal", "Panchkula",
  "Panipat", "Rewari", "Rohtak", "Sirsa", "Sonipat",
  "Yamunanagar", "Chamba", "Hamirpur", "Kangra", "Kinnaur",
  "Kullu", "Lahul&Spiti", "Mandi", "Shimla", "Sirmaur",
  "Solan", "Una", "Anantnag", "Badgam", "Bandipore",
  "Baramulla", "Doda", "Ganderbal", "Jammu", "Kargil",
  "Kathua", "Kishtwar", "Kulgam", "Kupwara", "Leh(Ladakh)",
  "Poonch", "Pulwama", "Rajouri", "Ramban", "Reasi",
  "Samba", "Shupiyan", "Srinagar", "Udhampur", "Bokaro",
  "Chatra", "Deoghar", "Dhanbad", "Dumka", "Garhwa",
  "Giridih", "Godda", "Gumla", "Hazaribagh", "Jamtara",
  "Khunti", "Kodarma", "Latehar", "Lohardaga", "Pakur",
  "Palamu", "PashchimiSinghbhum", "PurbiSinghbhum", "Ramgarh", "Ranchi",
  "Sahibganj", "Saraikela-kharsawan", "Simdega", "Bagalkot", "Bangalore",
  "BangaloreRural", "Belgaum", "Bellary", "Bidar", "Chamrajnagar",
  "Chikballapura", "Chikmagalur", "Chitradurga", "DakshinaKannada", "Davanagere",
  "Dharwad", "Gadag", "Gulbarga", "Hassan", "Haveri",
  "Kodagu", "Kolar", "Koppal", "Mandya", "Mysore",
  "Raichur", "Ramanagara", "Shimoga", "Tumkur", "Udupi",
  "UttaraKannada", "Yadgir", "Alappuzha", "Ernakulam", "Idukki",
  "Kannur", "Kasaragod", "Kollam", "Kottayam", "Kozhikode",
  "Malappuram", "Palakkad", "Pathanamthitta", "Thiruvananthapuram", "Thrissur",
  "Wayanad", "Lakshadweep", "AgarMalwa", "Alirajpur", "Anuppur",
  "Ashoknagar", "Balaghat", "Barwani", "Betul", "Bhind",
  "Bhopal", "Burhanpur", "Chhatarpur", "Chhindwara", "Damoh",
  "Datia", "Dewas", "Dhar", "Dindori", "EastNimar",
  "Guna", "Gwalior", "Harda", "Hoshangabad", "Indore",
  "Jabalpur", "Jhabua", "Katni", "Mandla", "Mandsaur",
  "Morena", "Narsimhapur", "Neemuch", "Panna", "Raisen",
  "Rajgarh", "Ratlam", "Rewa", "Sagar", "Satna",
  "Sehore", "Seoni", "Shahdol", "Shajapur", "Sheopur",
  "Shivpuri", "Sidhi", "Singrauli", "Tikamgarh", "Ujjain",
  "Umaria", "Vidisha", "WestNimar", "Ahmadnagar", "Akola",
  "Amravati", "Bhandara", "Bid", "Buldana", "Chandrapur",
  "Dhule", "Garhchiroli", "Gondiya", "Hingoli", "Jalgaon",
  "Jalna", "Kolhapur", "Latur", "MumbaiCity", "MumbaiSuburban",
  "Nagpur", "Nanded", "Nandurbar", "Nashik", "Osmanabad",
  "Palghar", "Parbhani", "Pune", "Ratnagiri", "Sangli",
  "Satara", "Sindhudurg", "Solapur", "Thane", "Wardha",
  "Washim", "Yavatmal", "Bishnupur", "Chandel", "Churachandpur",
  "ImphalEast", "ImphalWest", "Senapati", "Tamenglong", "Thoubal",
  "Ukhrul", "EastGaroHills", "EastKhasiHills", "JaintiaHills", "NorthGaroHills",
  "RiBhoi", "SouthGaroHills", "SouthWestGaroHills", "SouthWestKhasiHills", "WestGaroHills",
  "WestKhasiHills", "Aizawl", "Champhai", "Kolasib", "Lawangtlai",
  "Lunglei", "Mamit", "Saiha", "Serchhip", "Dimapur",
  "Kiphire", "Kohima", "Longleng", "Mokokchung", "Mon",
  "Peren", "Phek", "Tuensang", "Wokha", "Zunheboto",
  "West", "Anugul", "Balangir", "Baleshwar", "Bargarh",
  "Bauda", "Bhadrak", "Cuttack", "Debagarh", "Dhenkanal",
  "Gajapati", "Ganjam", "Jagatsinghapur", "Jajapur", "Jharsuguda",
  "Kalahandi", "Kandhamal", "Kendrapara", "Kendujhar", "Khordha",
  "Koraput", "Malkangiri", "Mayurbhanj", "Nabarangapur", "Nayagarh",
  "Nuapada", "Puri", "Rayagada", "Sambalpur", "Subarnapur",
  "Sundargarh", "Karaikal", "Mahe", "Puducherry", "Yanam",
  "Amritsar", "Barnala", "Bathinda", "Faridkot", "FatehgarhSahib",
  "Fazilka", "Firozpur", "Gurdaspur", "Hoshiarpur", "Jalandhar",
  "Kapurthala", "Ludhiana", "Mansa", "Moga", "Muktsar",
  "Pathankot", "Patiala", "Rupnagar", "SahibzadaAjitSinghNagar", "Sangrur",
  "ShahidBhagatSinghNagar", "TarnTaran", "Ajmer", "Alwar", "Banswara",
  "Baran", "Barmer", "Bharatpur", "Bhilwara", "Bikaner",
  "Bundi", "Chittaurgarh", "Churu", "Dausa", "Dhaulpur",
  "Dungarpur", "Ganganagar", "Hanumangarh", "Jaipur", "Jaisalmer",
  "Jalor", "Jhalawar", "Jhunjhunun", "Jodhpur", "Karauli",
  "Kota", "Nagaur", "Pali", "Pratapgarh", "Rajsamand",
  "SawaiMadhopur", "Sikar", "Sirohi", "Tonk", "Udaipur",
  "EastSikkim", "NorthSikkim", "SouthSikkim", "WestSikkim", "Ariyalur",
  "Chennai", "Coimbatore", "Cuddalore", "Dharmapuri", "Dindigul",
  "Erode", "Kancheepuram", "Kanniyakumari", "Karur", "Krishnagiri",
  "Madurai", "Nagappattinam", "Namakkal", "Perambalur", "Pudukkottai",
  "Ramanathapuram", "Salem", "Sivaganga", "Thanjavur", "TheNilgiris",
  "Theni", "Thiruvallur", "Thiruvarur", "Thoothukkudi", "Tiruchirappalli",
  "Tirunelveli", "Tiruppur", "Tiruvannamalai", "Vellore", "Viluppuram",
  "Virudunagar", "Adilabad", "Hyderabad", "Karimnagar", "Khammam",
  "Mahbubnagar", "Medak", "Nalgonda", "Nizamabad", "RangaReddy",
  "Warangal", "Dhalai", "Gomati", "Khowai", "NorthTripura",
  "Sipahijala", "SouthTripura", "Unokoti", "WestTripura", "Agra",
  "Aligarh", "Allahabad", "AmbedkarNagar", "Amethi", "Amroha",
  "Auraiya", "Azamgarh", "Baghpat", "Bahraich", "Ballia",
  "Banda", "Barabanki", "Bareilly", "Basti", "Bijnor",
  "Budaun", "Bulandshahr", "Chandauli", "Chitrakoot", "Deoria",
  "Etah", "Etawah", "Faizabad", "Farrukhabad", "Fatehpur",
  "Firozabad", "GautamBuddhaNagar", "Ghaziabad", "Ghazipur", "Gonda",
  "Gorakhpur", "Hapur", "Hardoi", "Hathras", "Jalaun",
  "Jaunpur", "Jhansi", "Kannauj", "KanpurDehat", "KanpurNagar",
  "Kasganj", "Kaushambi", "Kushinagar", "LakhimpurKheri", "Lalitpur",
  "Lucknow", "Maharajganj", "Mahoba", "Mainpuri", "Mathura",
  "Mau", "Meerut", "Mirzapur", "Moradabad", "Muzaffarnagar",
  "Pilibhit", "RaeBareli", "Rampur", "Saharanpur", "Sambhal",
  "SantKabirNagar", "SantRaviDasNagar", "Shahjahanpur", "Shamli", "Shravasti",
  "SiddharthNagar", "Sitapur", "Sonbhadra", "Sultanpur", "Unnao",
  "Varanasi", "Almora", "Bageshwar", "Chamoli", "Champawat",
  "Dehradun", "Garhwal", "Hardwar", "Nainital", "Pithoragarh",
  "Rudraprayag", "TehriGarhwal", "UdhamSinghNagar", "Uttarkashi", "Alipurduar",
  "Bankura", "Barddhaman", "Birbhum", "DakshinDinajpur", "Darjiling",
  "Haora", "Hugli", "Jalpaiguri", "KochBihar", "Kolkata",
  "Maldah", "Murshidabad", "Nadia", "North24Parganas", "PashchimMedinipur",
  "PurbaMedinipur", "Puruliya", "South24Parganas", "UttarDinajpur"
)
```



```{r}
# Compare the vectors
same_length <- length(nfhs_district_names) == length(gadm_district_names)
same_length
```


```{r}
common_districts <- intersect(nfhs_district_names, gadm_district_names)

# Print the common districts
print("Common Districts:")
print(common_districts)
```


```{r}
# Identify mismatched districts
nfhs_not_in_gadm <- setdiff(nfhs_district_names, gadm_district_names)
gadm_not_in_nfhs <- setdiff(gadm_district_names, nfhs_district_names)

# Print the results
cat("Number of districts in NFHS not in GADM: ", length(nfhs_not_in_gadm), "\n")
cat("Number of districts in GADM not in NFHS: ", length(gadm_not_in_nfhs), "\n")
```


```{r}

library(stringdist)

# Perform fuzzy matching with a threshold for string similarity
fuzzy_matches <- sapply(nfhs_not_in_gadm, function(x) {
  match <- amatch(x, gadm_not_in_nfhs, maxDist = 2) 
  if (!is.na(match)) {
    return(c(NFHS = x, GADM = gadm_not_in_nfhs[match]))
  } else {
    return(NULL)
  }
})

# Filter out the NULL matches
fuzzy_matches <- do.call(rbind, fuzzy_matches)

# Print the fuzzy matches
print("Potential fuzzy matches between NFHS and GADM:")
print(fuzzy_matches)

```

```{r}
# Create a dictionary for mapping GADM district names to NFHS district names
gadm_to_nfhs_map <- list(
  "Poonch" = "Punch",
  "Baramulla" = "Baramula",
  "Lahul&Spiti" = "Lahul & Spiti",
  "FatehgarhSahib" = "Fatehgarh Sahib",
  "TarnTaran" = "Tarn Taran",
  "TehriGarhwal" = "Tehri Garhwal",
  "UdhamSinghNagar" = "Udham Singh Nagar",
  "SawaiMadhopur" = "Sawai Madhopur",
  "GautamBuddhaNagar" = "Gautam Buddha Nagar",
  "KanpurDehat" = "Kanpur Dehat",
  "KanpurNagar" = "Kanpur Nagar",
  "Barabanki" = "Bara Banki",
  "AmbedkarNagar" = "Ambedkar Nagar",
  "Shravasti" = "Shrawasti",
  "SiddharthNagar" = "Siddharthnagar",
  "SantKabirNagar" = "Sant Kabir Nagar",
  "Maharajganj" = "Mahrajganj",
  "PashchimChamparan" = "Pashchim Champaran",
  "PurbaChamparan" = "Purba Champaran",
  "WestKameng" = "West Kameng",
  "EastKameng" = "East Kameng",
  "PapumPare" = "Papum Pare",
  "UpperSubansiri" = "Upper Subansiri",
  "UpperSiang" = "Upper Siang",
  "LowerSubansiri" = "Lower Subansiri",
  "DibangValley" = "Dibang Valley",
  "LowerDibangValley" = "Lower Dibang Valley",
  "ImphalWest" = "Imphal West",
  "ImphalEast" = "Imphal East",
  "Lawangtlai" = "Lawngtlai",
  "SouthGaroHills" = "South Garo Hills",
  "RiBhoi" = "Ribhoi",
  "EastKhasiHills" = "East Khasi Hills",
  "DimaHasao" = "Dima Hasao",
  "KamrupMetropolitan" = "Kamrup Metropolitan",
  "KochBihar" = "Koch Bihar",
  "UttarDinajpur" = "Uttar Dinajpur",
  "DakshinDinajpur" = "Dakshin Dinajpur",
  "PashchimMedinipur" = "Paschim Medinipur",
  "PurbaMedinipur" = "Purba Medinipur",
  "PurbiSinghbhum" = "Purbi Singhbhum",
  "PashchimiSinghbhum" = "Pashchimi Singhbhum",
  "Saraikela-kharsawan" = "Saraikela-Kharsawan",
  "Bauda" = "Baudh",
  "Janjgir-Champa" = "Janjgir - Champa",
  "UttarBastarKanker" = "Uttar Bastar Kanker",
  "BanasKantha" = "Banas Kantha",
  "Dahod" = "Dohad",
  "TheDangs" = "The Dangs",
  "Garhchiroli" = "Gadchiroli",
  "MumbaiSuburban" = "Mumbai Suburban",
  "EastGodavari" = "East Godavari",
  "WestGodavari" = "West Godavari",
  "UttaraKannada" = "Uttara Kannada",
  "DakshinaKannada" = "Dakshina Kannada",
  "Chamrajnagar" = "Chamarajanagar",
  "Chikballapura" = "Chikkaballapura",
  "BangaloreRural" = "Bangalore Rural",
  "NorthGoa" = "North Goa",
  "SouthGoa" = "South Goa",
  "TheNilgiris" = "The Nilgiris",
  "Nagappattinam" = "Nagapattinam",
  "Virudunagar" = "Virudhunagar",
  "SouthAndaman" = "South Andaman",
  "EastSiang" = "East Siang",
  "KurungKumey" = "Kurung Kumey",
  "WestSiang" = "West Siang",
  "KarbiAnglong" = "Karbi Anglong",
  "BalodaBazar" = "Baloda Bazar",
  "Gariaband" = "Gariyaband",
  "Kondagaon" = "Kodagaon",
  "Aravalli" = "Aravali",
  "ChhotaUdaipur" = "Chhota Udaipur",
  "DevbhumiDwarka" = "Devbhumi Dwarka",
  "GirSomnath" = "Gir Somnath",
  "PanchMahals" = "Panch Mahals",
  "SabarKantha" = "Sabar Kantha",
  "AgarMalwa" = "Agar Malwa",
  "EastGaroHills" = "East Garo Hills",
  "NorthGaroHills" = "North Garo Hills",
  "WestGaroHills" = "West Garo Hills",
  "WestKhasiHills" = "West Khasi Hills",
  "Mahbubnagar" = "Mahabubnagar",
  "RangaReddy" = "Ranga Reddy",
  "NorthTripura" = "North Tripura",
  "Sipahijala" = "Sepahijala",
  "SouthTripura" = "South Tripura",
  "Unokoti" = "Unakoti",
  "WestTripura" = "West Tripura",
  "RaeBareli" = "Rae Bareli",
  "ShahidBhagatSinghNagar" = "Shahid Bhagat Singh Nagar",
  "SahibzadaAjitSinghNagar" = "Sahibzada Ajit Singh Nagar",
  "LakhimpurKheri" = "Kheri",
  "DadraandNagarHaveli" = "Dadra & Nagar Haveli",
  "MumbaiCity" = "Mumbai",
  "NorthandMiddleAndaman" = "North & Middle Andaman",
  "NicobarIslands" = "Nicobars",
  "Nellore" = "Sri Potti Sriramulu Nellore",
  "North24Parganas" = "North Twenty Four Parganas",
  "South24Parganas" = "South Twenty Four Parganas",
  "Barddhaman" = "Purba Barddhaman",
  "EastNimar" = "Khandwa (East Nimar)",
  "Kaimur" = "Kaimur (Bhabua)",
  "WestNimar" = "Khargone (West Nimar)",
  "JaintiaHills" = "East Jantia Hills",
  "SouthWestGaroHills" = "South West Garo Hills",
  "SantRaviDasNagar" = "Sant Ravidas Nagar (Bhadohi)",
  "Hathras" = "Mahamaya Nagar",
  "Kasganj" = "Kanshiram Nagar",
  "Warangal" = "Warangal Rural",
  "Amroha" = "Jyotiba Phule Nagar",
  "NorthSikkim" = "North District",
  "SouthSikkim" = "South District",
  "EastSikkim" = "East District",
  "WestSikkim" = "West District",
  "SouthWestKhasiHills" = "South West Khasi Hills"
)

# Convert to a named vector for easier replacement
gadm_to_nfhs_map <- unlist(gadm_to_nfhs_map)

# Update the Names_2 column
india_districts <- india_districts %>%
  mutate(NAME_2 = ifelse(NAME_2 %in% names(gadm_to_nfhs_map), gadm_to_nfhs_map[NAME_2], NAME_2))

# Print the updated names for verification
print("Updated NAME_2 column:")
print(india_districts$NAME_2)

```


```{r}
# Load the writexl package
library(writexl)

# Convert the spatial data frame to a regular data frame if needed
india_districts_df <- as.data.frame(india_districts)

# Write the data frame to an Excel file
write_xlsx(india_districts_df, "updated_india_districts.xlsx")
```



```{r}

# Extract the updated district names from the spatial dataset
gadm_district_names_updated <- india_districts$NAME_2

# Find the districts in NFHS not in GADM
nfhs_not_in_gadm <- setdiff(nfhs_district_names, gadm_district_names_updated)

# Find the districts in GADM not in NFHS
gadm_not_in_nfhs <- setdiff(gadm_district_names_updated, nfhs_district_names)

# Print the results
cat("Number of districts in NFHS not in GADM: ", length(nfhs_not_in_gadm), "\n")
cat("Number of districts in GADM not in NFHS: ", length(gadm_not_in_nfhs), "\n")
```


```{r}
# Print the names of the districts
cat("Districts in NFHS not in GADM: ", nfhs_not_in_gadm, "\n")
```


```{r}
cat("Districts in GADM not in NFHS: ", gadm_not_in_nfhs, "\n")

```

```{r}
length(india_districts$NAME_2)
```


```{r}
# Load necessary libraries
library(dplyr)
library(ggplot2)
library(sf)

# Filter the spatial data for Kerala
kerala_districts <- india_districts %>% 
  filter(NAME_1 == "Kerala")

# Define the mapping for Kerala districts
kerala_mapping <- data.frame(
  sdist = c(588, 589, 590, 591, 592, 593, 594, 595, 596, 597, 598, 599, 600, 601),
  district_name = c("Kasaragod", "Kannur", "Wayanad", "Kozhikode", "Malappuram", 
                    "Palakkad", "Thrissur", "Ernakulam", "Idukki", "Kottayam", 
                    "Alappuzha", "Pathanamthitta", "Kollam", "Thiruvananthapuram"),
  stringsAsFactors = FALSE
)

# Filter the prevalence data for Kerala
kerala_prevalence <- district_prevalence_true %>% 
  filter(sdist %in% kerala_mapping$sdist) %>%
  left_join(kerala_mapping, by = "sdist") %>%
  select(district_name, `I(m19 < 2500)TRUE`) %>%
  rename(prevalence = `I(m19 < 2500)TRUE`)

# Join the spatial data with the prevalence data
kerala_districts <- kerala_districts %>% 
  left_join(kerala_prevalence, by = c("NAME_2" = "district_name"))

# Plot the map
ggplot(kerala_districts) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "Low Birth Weight Prevalence in Kerala",
       fill = "Prevalence (%)") +
  theme_minimal()



# Filter the spatial data for Andaman and Nicobar
andaman_districts <- india_districts %>% 
  filter(NAME_1 == "AndamanandNicobar")

# Define the mapping for Andaman and Nicobar districts
andaman_mapping <- data.frame(
  sdist = c(638, 639, 640),
  district_name = c("Nicobars", "North & Middle Andaman", "South Andaman"),
  stringsAsFactors = FALSE
)

# Filter the prevalence data for Andaman and Nicobar
andaman_prevalence <- district_prevalence_true %>% 
  filter(sdist %in% andaman_mapping$sdist) %>%
  left_join(andaman_mapping, by = "sdist") %>%
  select(district_name, `I(m19 < 2500)TRUE`) %>%
  rename(prevalence = `I(m19 < 2500)TRUE`)

# Join the spatial data with the prevalence data
andaman_districts <- andaman_districts %>% 
  left_join(andaman_prevalence, by = c("NAME_2" = "district_name"))

# Plot the map
ggplot(andaman_districts) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "Low Birth Weight Prevalence in Andaman and Nicobar",
       fill = "Prevalence (%)") +
  theme_minimal()




# Filter the spatial data for Andhra Pradesh
andhra_districts <- india_districts %>% 
  filter(NAME_1 == "AndhraPradesh")

# Define the mapping for Andhra Pradesh districts
andhra_mapping <- data.frame(
  sdist = c(542, 543, 544, 545, 546, 547, 548, 549, 550, 551, 552, 553, 554),
  district_name = c("Srikakulam", "Vizianagaram", "Visakhapatnam", "East Godavari", 
                    "West Godavari", "Krishna", "Guntur", "Prakasam", 
                    "Sri Potti Sriramulu Nellore", "Y.S.R.", "Kurnool", "Anantapur", "Chittoor"),
  stringsAsFactors = FALSE
)

# Filter the prevalence data for Andhra Pradesh
andhra_prevalence <- district_prevalence_true %>% 
  filter(sdist %in% andhra_mapping$sdist) %>%
  left_join(andhra_mapping, by = "sdist") %>%
  select(district_name, `I(m19 < 2500)TRUE`) %>%
  rename(prevalence = `I(m19 < 2500)TRUE`)

# Join the spatial data with the prevalence data
andhra_districts <- andhra_districts %>% 
  left_join(andhra_prevalence, by = c("NAME_2" = "district_name"))

# Plot the choropleth map
ggplot(andhra_districts) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "Low Birth Weight Prevalence by District in Andhra Pradesh",
       fill = "Prevalence (%)") +
  theme_minimal()




# Filter the spatial data for Arunachal Pradesh
arunachal_districts <- india_districts %>% 
  filter(NAME_1 == "ArunachalPradesh")

# Define the mapping for Arunachal Pradesh districts
arunachal_mapping <- data.frame(
  sdist = c(245, 246, 247, 248, 249, 252, 801, 802, 803, 804, 805, 806, 808, 809),
  district_name = c("Tawang", "West Kameng", "East Kameng", "Papum Pare", 
                    "Upper Subansiri", "Upper Siang", "East Siang", "Kra Daadi", 
                    "Kurung Kumey", "Lohit", "Longding", "Namsai", 
                    "Tirap", "West Siang"),
  stringsAsFactors = FALSE
)

# Filter the prevalence data for Arunachal Pradesh
arunachal_prevalence <- district_prevalence_true %>% 
  filter(sdist %in% arunachal_mapping$sdist) %>%
  left_join(arunachal_mapping, by = "sdist") %>%
  select(district_name, `I(m19 < 2500)TRUE`) %>%
  rename(prevalence = `I(m19 < 2500)TRUE`)

# Join the spatial data with the prevalence data
arunachal_districts <- arunachal_districts %>% 
  left_join(arunachal_prevalence, by = c("NAME_2" = "district_name"))

# Plot the choropleth map
ggplot(arunachal_districts) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "Low Birth Weight Prevalence in Arunachal Pradesh",
       fill = "Prevalence (%)") +
  theme_minimal()


# Filter the spatial data for Goa
goa_districts <- india_districts %>% 
  filter(NAME_1 == "Goa")

# Define the mapping for Goa districts
goa_mapping <- data.frame(
  sdist = c(585, 586),
  district_name = c("North Goa", "South Goa"),
  stringsAsFactors = FALSE
)

# Filter the prevalence data for Goa
goa_prevalence <- district_prevalence_true %>% 
  filter(sdist %in% goa_mapping$sdist) %>%
  left_join(goa_mapping, by = "sdist") %>%
  select(district_name, `I(m19 < 2500)TRUE`) %>%
  rename(prevalence = `I(m19 < 2500)TRUE`)

# Join the spatial data with the prevalence data
goa_districts <- goa_districts %>% 
  left_join(goa_prevalence, by = c("NAME_2" = "district_name"))

# Plot the choropleth map
ggplot(goa_districts) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "Low Birth Weight Prevalence by District in Goa",
       fill = "Prevalence (%)") +
  theme_minimal()



```

```{r}

# Filter the spatial data for West Bengal
west_bengal_districts <- india_districts %>% 
  filter(NAME_1 == "WestBengal")

# Define the mapping for West Bengal districts
west_bengal_mapping <- data.frame(
  sdist = c(932, 327, 328, 329, 330, 331, 332, 333, 334, 336, 337, 338, 339, 340, 341, 342, 343, 344, 345),
  district_name = c("Purba Barddhaman", "Darjiling", "Jalpaiguri", "Koch Bihar", "Uttar Dinajpur", 
                    "Dakshin Dinajpur", "Maldah", "Murshidabad", "Birbhum", "Nadia", 
                    "North Twenty Four Parganas", "Hugli", "Bankura", "Puruliya", 
                    "Haora", "Kolkata", "South Twenty Four Parganas", 
                    "Paschim Medinipur", "Purba Medinipur"),
  stringsAsFactors = FALSE
)

# Filter the prevalence data for West Bengal
west_bengal_prevalence <- district_prevalence_true %>% 
  filter(sdist %in% west_bengal_mapping$sdist) %>%
  left_join(west_bengal_mapping, by = "sdist") %>%
  select(district_name, `I(m19 < 2500)TRUE`) %>%
  rename(prevalence = `I(m19 < 2500)TRUE`)

# Join the spatial data with the prevalence data
west_bengal_districts <- west_bengal_districts %>% 
  left_join(west_bengal_prevalence, by = c("NAME_2" = "district_name"))

# Plot the choropleth map
ggplot(west_bengal_districts) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "Low Birth Weight Prevalence in West Bengal",
       fill = "Prevalence (%)") +
  theme_minimal()





# Filter the spatial data for Assam
assam_districts <- india_districts %>% 
  filter(NAME_1 == "Assam")

# Define the mapping for Assam districts
assam_mapping <- data.frame(
  sdist = c(812, 814, 815, 817, 818, 819, 300, 302, 303, 304, 307, 308, 309, 310, 313, 315, 316, 317, 318, 319, 320, 321, 322, 323, 324, 325, 326),
  district_name = c("Dhubri", "Jorhat", "Karbi Anglong", "Nagaon", "Sivasagar", "Sonitpur", 
                    "Kokrajhar", "Goalpara", "Barpeta", "Morigaon", "Lakhimpur", "Dhemaji", 
                    "Tinsukia", "Dibrugarh", "Golaghat", "Dima Hasao", "Cachar", "Karimganj", 
                    "Hailakandi", "Bongaigaon", "Chirang", "Kamrup", "Kamrup Metropolitan", 
                    "Nalbari", "Baksa", "Darrang", "Udalguri"),
  stringsAsFactors = FALSE
)

# Filter the prevalence data for Assam
assam_prevalence <- district_prevalence_true %>% 
  filter(sdist %in% assam_mapping$sdist) %>%
  left_join(assam_mapping, by = "sdist") %>%
  select(district_name, `I(m19 < 2500)TRUE`) %>%
  rename(prevalence = `I(m19 < 2500)TRUE`)

# Join the spatial data with the prevalence data
assam_districts <- assam_districts %>% 
  left_join(assam_prevalence, by = c("NAME_2" = "district_name"))

# Plot the choropleth map
ggplot(assam_districts) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "Low Birth Weight Prevalence  in Assam",
       fill = "Prevalence (%)") +
  theme_minimal()



# Filter the spatial data for Himachal Pradesh
hp_districts <- india_districts %>%
  filter(NAME_1 == "HimachalPradesh")

# Handle duplicate entries for Lahul & Spiti and Kinnaur by merging their geometries
hp_districts <- hp_districts %>%
  group_by(NAME_2) %>%
  summarize(geometry = st_union(geometry))

# Define the mapping for Himachal Pradesh districts
hp_mapping <- data.frame(
  sdist = c(23, 24, 25, 26, 27, 28, 29, 30, 31, 32, 33, 34),
  district_name = c("Chamba", "Kangra", "Lahul & Spiti", "Kullu", "Mandi", "Hamirpur", "Una",
                    "Bilaspur", "Solan", "Sirmaur", "Shimla", "Kinnaur"),
  stringsAsFactors = FALSE
)

# Filter the prevalence data for Himachal Pradesh
hp_prevalence <- district_prevalence_true %>%
  filter(sdist %in% hp_mapping$sdist) %>%
  left_join(hp_mapping, by = "sdist") %>%
  select(district_name, `I(m19 < 2500)TRUE`) %>%
  rename(prevalence = `I(m19 < 2500)TRUE`)

# Join the spatial data with the prevalence data
hp_districts <- hp_districts %>%
  left_join(hp_prevalence, by = c("NAME_2" = "district_name"))

# Plot the choropleth map
ggplot(hp_districts) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "Low Birth Weight Prevalence by District in Himachal Pradesh",
       fill = "Prevalence (%)") +
  theme_minimal()


# Filter the spatial data for Lakshadweep
lakshadweep_districts <- india_districts %>%
  filter(NAME_1 == "Lakshadweep")

# Define the mapping for Lakshadweep districts
lakshadweep_mapping <- data.frame(
  sdist = 587,
  district_name = "Lakshadweep",
  stringsAsFactors = FALSE
)

# Filter the prevalence data for Lakshadweep
lakshadweep_prevalence <- district_prevalence_true %>%
  filter(sdist == 587) %>%
  left_join(lakshadweep_mapping, by = "sdist") %>%
  select(district_name, `I(m19 < 2500)TRUE`) %>%
  rename(prevalence = `I(m19 < 2500)TRUE`)

# Join the spatial data with the prevalence data
lakshadweep_districts <- lakshadweep_districts %>%
  left_join(lakshadweep_prevalence, by = c("NAME_2" = "district_name"))

# Plot the choropleth map
ggplot(lakshadweep_districts) +
  geom_sf(aes(fill = prevalence)) +
  scale_fill_viridis_c() +
  labs(title = "Low Birth Weight Prevalence in Lakshadweep",
       fill = "Prevalence (%)") +
  theme_minimal()


```






























































